Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices

### 2017-03-02 Meetings/GPMNov2016/gpm_november2016_vianello.tex
changes in the structure of the folder plus addition of KoM presentation

\documentclass[10pt, compress]{beamer}
\usetheme[conference=MST1-EPM,venue=Garching, date=15/11/2016, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{../beamerclass/tangocolors}
\usepackage{../beamerclass/rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{../beamerclass/onimage}
\usepackage[export]{adjustbox}
\usepackage{bm}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{Filamentary transport in high-power H-mode conditions and in
  no/small-ELM regimes to predict heat and particle loads on PFCs for
  future devices}
\date{15 November 2016}
\author[Topic 21. J. Madsen and N.Vianello]{J. Madsen and N. Vianello}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle

@@

\section{Background}
\begin{frame}{Present status}
  \setbeamercovered{transparent}
  \begin{enumerate}[<+(1) | invisible@-+>]
    \item Experimental and theoretical investigations suggest that SOL density profiles are
      determined by the balance between radial filamentary transport and parallel dynamics
    \item The balance changes at high density and leads to broadened SOL density profiles $\rightarrow$ \emph{shoulder formation}
    \item This is observed in L-mode plasmas in a variety of devices including AUG \parencite{Carralero:2014gs},
      TCV \parencite{Garcia:2007p2615} and MAST \parencite{Militello:2016hk}
    \item Observations exhibit various other dependencies e.g., divertor
      collisionality, plasma current, seeding. \alert{Results from
        different devices not fully reconciled and the underlying mechanism is not fully understood.}
    \item Studies of shoulder formation in H-Mode are so far limited 
	%\item Particle and energy transport in the SOL is crucial for lifetime of PFC in ITER and DEMO
%    \item First we will report a summary of the achievements and then
 %    personal comments and plans
    \end{enumerate}
\end{frame}
\section{L-Mode}
\begin{frame}{L-Mode studies: AUG/1}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item<1-> AUG and JET \parencite{Carralero:2015gu} suggest that divertor collisionality 
        \begin{equation*}
        \Lambda_{div} = \frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}
      \end{equation*}
      controls filaments size
        \item<2-> \textcolor{red}{Tested by changing n$_e$
            and $T_e$ through fueling/seeding/heating}
        \item<3-> This determines a change of the velocity-size
          scaling from
            \textcolor{ta3chameleon}{sheath-limited}
        to \textcolor{blue}{inertial regime}.
       \onslide<4->{\alert{$\Lambda_{div}$ rules the density profile scale
           length}}
       \item<5> This finally determines the shoulder formation
        \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \only<1-2>{
      \begin{tikzonimage}[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroPRL15a}
          \draw [thick, ta3chameleon, thick, rotate=1] (0.43,0.25) ellipse (0.23 and 0.1);
          \draw [thick, blue, thick, rotate=-4] (0.8,0.55) ellipse (0.1 and 0.33);
        \only<2>{
          \draw [ultra thick, red, thick, dashed] (0.5,0.63) circle (0.12);
        }
      \end{tikzonimage}}
    \only<3-4>{
      \begin{tikzonimage}[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroPRL15b}
          \draw [ultra thick, ta3chameleon, rotate=1] (0.2,0.5) ellipse (0.05 and 0.4);
          \draw [thick, blue, rotate=15] (0.65,0.07) ellipse (0.4 and 0.1);
      \end{tikzonimage}
    }
    \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroPRL15c}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{L-Mode studies: AUG/2}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item<1-> Profile modified by an increase of blob-size and change of
        \alert{packing fraction: $f_{fil} = \nu_{fil}\tau_{AC}$}
        \onslide<2->{\textcolor{blue}{and filament relative density}
          {\footnotesize (Carralero 2016 in preparation)}}
      \item<3-> As a consequence the contribution of filaments to
        radial transport increases
      \item<4|only@4> \alert{Beware the change of frequency may be due to a
        modification of fluctuation velocity which is known to vary
        with densities ad normalized greenwald fraction \parencite{0029-5515-51-5-053020}}  
      \item<5> Parallel flow is strongly reduced whenever we increase
        the divertor collisionality
      \end{itemize}
    \end{column}
      \begin{column}{0.5\textwidth}
        \includegraphics<1>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16a}
        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16b}
        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16c}
        \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/AgostiniNF2011}
        \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16d}
      \end{column}
    \end{columns}
  \end{frame}

  \begin{frame}{L-Mode studies:AUG/3}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item<1-> Electron and ions behave differently
      \item<2|only@2> T$_{e, fil} \sim 1.2 $T$_{e, bk}$ roughly constant
        accross the SOL and slightly affected by the increase of
        divertor collisionality
      \item<3|only@3> Ions are strongly affected: for
        \textcolor{red}{$\Lambda_{div}<1$ T$_{i, fil} > $ T$_{i, bk}$
          and $\lambda_{T_i} \sim 30$
          mm}. \textcolor{blue}{$\Lambda_{div}>1$ T$_{i, fil} \sim $
          T$_{i, bk}\sim 25$ eV
          and $\lambda_{T_i} \sim 8$ mm}
       \item<4-> Ion energy spectrum from
         $\mathbf{E}\times\mathbf{B}$ analyzer shrinks towards lower
         energy for $\Lambda_{div} > 1$
       \item<5> EMC3-Eirene simulation suggests that such a reduction
         can't be accounted for thermalization process. An
         \alert{ionization front builds in front of the limiter shadow}   
       \end{itemize}
    \end{column}
      \begin{column}{0.5\textwidth}
        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16e}
        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16f}
        \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16g}
        \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16h}
      \end{column}
    \end{columns}
  \end{frame}

  \begin{frame}{L-Mode: TCV}
    \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item<1|only@1> Flexibility has allowed to test $\Lambda_{div}$
        dependence on L$_{\parallel}$ by varying flux expansion f$_x$:
        \begin{equation*}
          f_x = \frac{(B_p/B_t)_{MP}}{(B_p/B_t)_{SP}}
        \end{equation*}
        in ohmic density ramps \parencite{vianello:iaea2016}
      \item<2|only@2> Slight variation of density profiles at the target but
        due to direct dependence on L$_{\parallel}$ large increase of
        $\Lambda_{div}$. \alert{Upstream profiles only varies whenever
        we reach a certain amount of $\langle n_e \rangle$}
       \only<3-5>{\item Weak dependence of blob-size from $\Lambda_{div}$,
        \onslide<4-5>{\textcolor{red}{also on a statistical
            basis}}. \onslide<5>{Strong dependence on average density,
          independent of L$_{\parallel}$}}
       \item<6|only@6> $\lambda_n$ depends clearly on blob-size
         whereas the dependence on divertor condition is less
         obvious. \alert{$\Lambda_{div}$ necessary but not sufficient}
      \end{itemize}
    \end{column}
      \begin{column}{0.5\textwidth}
        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/VianelloIAEA16a}
        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/VianelloIAEA16b}
        \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/VianelloIAEA16c}
        \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/VianelloIAEA16d}
        \includegraphics<6>[width=\textwidth]{../pdfbox/KoM15Nov/VianelloIAEA16e}
      \end{column}
    \end{columns}
  \end{frame}

  \begin{frame}{L-Mode: JET}
    \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item<1|only@1> The shoulder formation strongly depends on
        divertor geometry, disappear with vertical target and strike
        point closest to cryogenics pumps \parencite{Wynn:EPS2016}
      \item<2|only@2> The midplane pressure from baratrons is
        equivalent between the different divertor. \alert{This would
          indicate that SOL neutral density at the outboard midplane does not play any role}
       \item<3|only@3> In the horizontal target configuration the
         results indicate that the shoulder forms right at the
         transition from sheath-limited to high-recycling where also
         $\Lambda_{div}$ strongly increase
       \item<4|only@4> Shoulder amplitude correlates with strike
         points position. \alert{Shoulder, ionization and
           $\Gamma_{ion, plate}$ larger when R$_{strike}$ smaller away
         from the pump}
       \item<5|only@5> In seeded discharges the transition observed at
         very high level of $\Lambda_{div} >> 1$
      \end{itemize}
    \end{column}
      \begin{column}{0.5\textwidth}
        \includegraphics<1>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16a}
        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16b}
        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16c}
        \includegraphics<4>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16d}
        \includegraphics<5>[width=\textwidth]{../pdfbox/KoM15Nov/LipschultzITPA16e}
      \end{column}
    \end{columns}
  \end{frame}

  \begin{frame}{L-Mode: MAST}
    \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item<1|only@1> Strong dependence on
        I$_p$ \parencite{Militello:2016hk}. Increasing I$_p$ at
        constant toroidal field shoulder disappears. Consistent with
        observation in other devices
      \item<2|only@2> Filaments binormal dimension increases with
        current \parencite{Kirk:2016jj} or equivalently decreases with L$_{\parallel}$
       \item<3|only@3> Filament radial velocity decreases with current
         as well as the radial dimension \parencite{Kirk:2016jj}
      \end{itemize}
    \end{column}
      \begin{column}{0.5\textwidth}
        \includegraphics<1>[width=\textwidth]{../pdfbox/KoM15Nov/MilitelloNF16a}
        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/KirkPPCF16a}
        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/KirkPPCF16c}
      \end{column}
    \end{columns}
  \end{frame}

  \section{H-Mode}
  \begin{frame}{AUG: H-Mode}
    \begin{columns}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
      \item<1|only@1> SOL profiles in H-Mode so far investigated on
        AUG \parencite{Muller:2015jt,Sun:2015bu,carralero:psi2016}
      \item<2|only@2> Differently from L-Mode, complete detachment
        suggested to be mandatory for increasing of $\lambda_n$ \parencite{Sun:2015bu}
       \item<3|only@3> In weak H-Mode \parencite{carralero:psi2016}
         shoulder depends on a combination of $\Lambda_{div}$ and
         fueling rate. Complete detachment seems instead not necessary
         although very weak shoulder
      \end{itemize}
    \end{column}
      \begin{column}{0.6\textwidth}
        \includegraphics<1>[width=\textwidth]{../pdfbox/KoM15Nov/MuellerJNM15a}
        \includegraphics<2>[width=\textwidth]{../pdfbox/KoM15Nov/SunPPCF15a}
        \includegraphics<3>[width=\textwidth]{../pdfbox/KoM15Nov/CarraleroMST16i}
      \end{column}
    \end{columns}
  \end{frame}

>>>>

\documentclass[10pt, compress]{beamer}
\usetheme[conference=KoM,venue=Remote, date=02/03/2017, titleprogressbar, logo=RFX-logo]{Eurof}
\usepackage{listings,amsmath,multimedia, amssymb}
\usepackage{../beamerclass/tangocolors}
\usepackage{../beamerclass/rfxcolor}
% for drawing
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,backgrounds}
\usepackage{../beamerclass/onimage}
\usepackage[export]{adjustbox}
\usepackage{bm}
% for font
\usepackage[absolute,overlay]{textpos}
  \setlength{\TPHorizModule}{1mm}
  \setlength{\TPVertModule}{1mm}

\usepackage[style=nature,citestyle=authoryear-comp,defernumbers=true,maxnames=2,firstinits=true,
uniquename=init,backend=bibtex8,arxiv=abs,mcite]{biblatex}
\bibliography{biblio}
\renewcommand*{\bibfont}{\footnotesize}
\renewcommand*{\citesetup}{\footnotesize}
\usepackage[export]{adjustbox}
\makeatother
\mode<presentation>
\makeatletter
% add a macro that saves its argument
\newcommand{\footlineextra}[1]{\gdef\insertfootlineextra{#1}}
\newbox\footlineextrabox
% for reducing font on a single slide
\newcommand\Fontvi{\fontsize{8}{7.2}\selectfont}
\title{Filamentary transport in high-power H-mode conditions and in
  no/small-ELM regimes to predict heat and particle loads on PFCs for
  future devices}
\date{03 March 2017}
\author[Topic 21. J. Madsen and N.Vianello]{J. Madsen and N. Vianello}
\begin{document}
\tikzstyle{every picture}+=[remember picture]
\maketitle

@@

\section{Background}
\begin{frame}{Present status}
  \setbeamercovered{transparent}
  \begin{enumerate}[<+(1) | invisible@-+>]
    \item Experimental and theoretical investigations suggest that SOL density profiles are
      determined by the balance between radial filamentary transport and parallel dynamics
    \item The balance changes at high density and leads to broadened SOL density profiles $\rightarrow$ \emph{shoulder formation}
    \item This is observed in L-mode plasmas in a variety of devices including AUG \parencite{Carralero:2014gs},
      TCV \parencite{Garcia:2007p2615} and MAST \parencite{Militello:2016hk}
    \item Observations exhibit various other dependencies e.g., divertor
      collisionality, plasma current, seeding. \alert{Results from
        different devices not fully reconciled and the underlying mechanism is not fully understood.}
    \item Studies of shoulder formation in H-Mode are so far limited 
	%\item Particle and energy transport in the SOL is crucial for lifetime of PFC in ITER and DEMO
%    \item First we will report a summary of the achievements and then
 %    personal comments and plans
    \end{enumerate}
\end{frame}
\section{L-Mode}
\begin{frame}{L-Mode studies: AUG/1}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item<1-> AUG and JET \parencite{Carralero:2015gu} suggest that divertor collisionality 
        \begin{equation*}
        \Lambda_{div} = \frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}
      \end{equation*}
      controls filaments size
        \item<2-> \textcolor{red}{Tested by changing n$_e$
            and $T_e$ through fueling/seeding/heating}
        \item<3-> This determines a change of the velocity-size
          scaling from
            \textcolor{ta3chameleon}{sheath-limited}
        to \textcolor{blue}{inertial regime}.
       \onslide<4->{\alert{$\Lambda_{div}$ rules the density profile scale
           length}}
       \item<5> This finally determines the shoulder formation
        \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \only<1-2>{
      \begin{tikzonimage}[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroPRL15a}
          \draw [thick, ta3chameleon, thick, rotate=1] (0.43,0.25) ellipse (0.23 and 0.1);
          \draw [thick, blue, thick, rotate=-4] (0.8,0.55) ellipse (0.1 and 0.33);
        \only<2>{
          \draw [ultra thick, red, thick, dashed] (0.5,0.63) circle (0.12);
        }
      \end{tikzonimage}}
    \only<3-4>{
      \begin{tikzonimage}[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroPRL15b}
          \draw [ultra thick, ta3chameleon, rotate=1] (0.2,0.5) ellipse (0.05 and 0.4);
          \draw [thick, blue, rotate=15] (0.65,0.07) ellipse (0.4 and 0.1);
      \end{tikzonimage}
    }
    \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroPRL15c}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{L-Mode studies: AUG/2}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item<1-> Profile modified by an increase of blob-size and change of
        \alert{packing fraction: $f_{fil} = \nu_{fil}\tau_{AC}$}
        \onslide<2->{\textcolor{blue}{and filament relative density}
          {\footnotesize (Carralero 2016 in preparation)}}
      \item<3-> As a consequence the contribution of filaments to
        radial transport increases
      \item<4|only@4> \alert{Beware the change of frequency may be due to a
        modification of fluctuation velocity which is known to vary
        with densities ad normalized greenwald fraction \parencite{0029-5515-51-5-053020}}  
      \item<5> Parallel flow is strongly reduced whenever we increase
        the divertor collisionality
      \end{itemize}
    \end{column}
      \begin{column}{0.5\textwidth}
        \includegraphics<1>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16a}
        \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16b}
        \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16c}
        \includegraphics<4>[width=\textwidth]{../../pdfbox/KoM15Nov/AgostiniNF2011}
        \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16d}
      \end{column}
    \end{columns}
  \end{frame}

  \begin{frame}{L-Mode studies:AUG/3}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item<1-> Electron and ions behave differently
      \item<2|only@2> T$_{e, fil} \sim 1.2 $T$_{e, bk}$ roughly constant
        accross the SOL and slightly affected by the increase of
        divertor collisionality
      \item<3|only@3> Ions are strongly affected: for
        \textcolor{red}{$\Lambda_{div}<1$ T$_{i, fil} > $ T$_{i, bk}$
          and $\lambda_{T_i} \sim 30$
          mm}. \textcolor{blue}{$\Lambda_{div}>1$ T$_{i, fil} \sim $
          T$_{i, bk}\sim 25$ eV
          and $\lambda_{T_i} \sim 8$ mm}
       \item<4-> Ion energy spectrum from
         $\mathbf{E}\times\mathbf{B}$ analyzer shrinks towards lower
         energy for $\Lambda_{div} > 1$
       \item<5> EMC3-Eirene simulation suggests that such a reduction
         can't be accounted for thermalization process. An
         \alert{ionization front builds in front of the limiter shadow}   
       \end{itemize}
    \end{column}
      \begin{column}{0.5\textwidth}
        \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16e}
        \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16f}
        \includegraphics<4>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16g}
        \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16h}
      \end{column}
    \end{columns}
  \end{frame}

  \begin{frame}{L-Mode: TCV}
    \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item<1|only@1> Flexibility has allowed to test $\Lambda_{div}$
        dependence on L$_{\parallel}$ by varying flux expansion f$_x$:
        \begin{equation*}
          f_x = \frac{(B_p/B_t)_{MP}}{(B_p/B_t)_{SP}}
        \end{equation*}
        in ohmic density ramps \parencite{vianello:iaea2016}
      \item<2|only@2> Slight variation of density profiles at the target but
        due to direct dependence on L$_{\parallel}$ large increase of
        $\Lambda_{div}$. \alert{Upstream profiles only varies whenever
        we reach a certain amount of $\langle n_e \rangle$}
       \only<3-5>{\item Weak dependence of blob-size from $\Lambda_{div}$,
        \onslide<4-5>{\textcolor{red}{also on a statistical
            basis}}. \onslide<5>{Strong dependence on average density,
          independent of L$_{\parallel}$}}
       \item<6|only@6> $\lambda_n$ depends clearly on blob-size
         whereas the dependence on divertor condition is less
         obvious. \alert{$\Lambda_{div}$ necessary but not sufficient}
      \end{itemize}
    \end{column}
      \begin{column}{0.5\textwidth}
        \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16a}
        \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16b}
        \includegraphics<4>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16c}
        \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16d}
        \includegraphics<6>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16e}
      \end{column}
    \end{columns}
  \end{frame}

  \begin{frame}{L-Mode: JET}
    \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item<1|only@1> The shoulder formation strongly depends on
        divertor geometry, disappear with vertical target and strike
        point closest to cryogenics pumps \parencite{Wynn:EPS2016}
      \item<2|only@2> The midplane pressure from baratrons is
        equivalent between the different divertor. \alert{This would
          indicate that SOL neutral density at the outboard midplane does not play any role}
       \item<3|only@3> In the horizontal target configuration the
         results indicate that the shoulder forms right at the
         transition from sheath-limited to high-recycling where also
         $\Lambda_{div}$ strongly increase
       \item<4|only@4> Shoulder amplitude correlates with strike
         points position. \alert{Shoulder, ionization and
           $\Gamma_{ion, plate}$ larger when R$_{strike}$ smaller away
         from the pump}
       \item<5|only@5> In seeded discharges the transition observed at
         very high level of $\Lambda_{div} >> 1$
      \end{itemize}
    \end{column}
      \begin{column}{0.5\textwidth}
        \includegraphics<1>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16a}
        \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16b}
        \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16c}
        \includegraphics<4>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16d}
        \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16e}
      \end{column}
    \end{columns}
  \end{frame}

  \begin{frame}{L-Mode: MAST}
    \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item<1|only@1> Strong dependence on
        I$_p$ \parencite{Militello:2016hk}. Increasing I$_p$ at
        constant toroidal field shoulder disappears. Consistent with
        observation in other devices
      \item<2|only@2> Filaments binormal dimension increases with
        current \parencite{Kirk:2016jj} or equivalently decreases with L$_{\parallel}$
       \item<3|only@3> Filament radial velocity decreases with current
         as well as the radial dimension \parencite{Kirk:2016jj}
      \end{itemize}
    \end{column}
      \begin{column}{0.5\textwidth}
        \includegraphics<1>[width=\textwidth]{../../pdfbox/KoM15Nov/MilitelloNF16a}
        \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/KirkPPCF16a}
        \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/KirkPPCF16c}
      \end{column}
    \end{columns}
  \end{frame}

  \section{H-Mode}
  \begin{frame}{AUG: H-Mode}
    \begin{columns}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
      \item<1|only@1> SOL profiles in H-Mode so far investigated on
        AUG \parencite{Muller:2015jt,Sun:2015bu,carralero:psi2016}
      \item<2|only@2> Differently from L-Mode, complete detachment
        suggested to be mandatory for increasing of $\lambda_n$ \parencite{Sun:2015bu}
       \item<3|only@3> In weak H-Mode \parencite{carralero:psi2016}
         shoulder depends on a combination of $\Lambda_{div}$ and
         fueling rate. Complete detachment seems instead not necessary
         although very weak shoulder
      \end{itemize}
    \end{column}
      \begin{column}{0.6\textwidth}
        \includegraphics<1>[width=\textwidth]{../../pdfbox/KoM15Nov/MuellerJNM15a}
        \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/SunPPCF15a}
        \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16i}
      \end{column}
    \end{columns}
  \end{frame}
